---
title: "ACTH and Dex DEG Analysis"
author: "Jeff Brabec"
date: "4/4/2022"
output: html_document
---

# I. Load packages and custom functions written for analysis
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(DESeq2)
library(gee)
library(janitor)
library(ggvenn)
library(patchwork)

#Load custom functions
fun.dir <- list.files(here("src"), full.names = TRUE)
for(i in 1:length(fun.dir)){source(fun.dir[i])}
```

# II. Read in and preprocess data

## Read in Counts data
```{r}
# read in the matrix we generated using htseq-count 
rat_dat <- as.matrix(read.table(here("data", "all_counts.txt"), 
                                sep="\t", 
                                header = TRUE, 
                                row.names=1, 
                                stringsAsFactors = F))

# filter out these last 5 rows; contain metadata info
rat_dat <- rat_dat[1:(nrow(rat_dat)-5),]

# read in the file from the SRA metadata that has sample/experimental labels 
rat_groups <- read.csv(here("data", "sample_groups.csv"))
```

## vehicle ELS baseline model
```{r}
# order by SRA run accession 
rat_groups_w_syn <- rat_groups %>% 
  arrange(samp_id) %>% 
  mutate(to_sep = samp_id) %>% 
  #filter(group != "syn_acth_els") %>% 
  separate(to_sep, into = c("region", "animal"), " ") %>%
  mutate(across(c(group, sex), as.factor),
         #region = ifelse(str_detect(samp_id, "Hip"), "Hip", "PFC"),
         region = as.factor(region),
         samp_id = str_replace_all(samp_id, fixed(" "), ""),
         animal = as.factor(animal)) %>% 
  mutate(treat_group = case_when(group == "acthar_els" | group == "syn_acth_els" ~ "ACTH",
                                 group == "dex_els" ~ "DEX",
                                 group == "ELS" ~ "ELS",
                                 group == "ctl" ~ "CTL"),
         treat_group = as.factor(treat_group)) %>% 
  arrange(animal) %>% 
  mutate(treat_group = fct_relevel(treat_group, c("ELS", "ACTH", "DEX", "CTL"))) # This line Sets ELS as first factor level


rat_deseq_dat_w_syn <- DESeqDataSetFromMatrix(countData = rat_dat,
                                              colData = rat_groups_w_syn,
                                              design = ~ group + sex)

keep_w_syn <- rowSums(counts(rat_deseq_dat_w_syn)) >= 10
rat_deseq_dat_w_syn <- rat_deseq_dat_w_syn[keep_w_syn,]

rat_deseq_dat_w_syn <- estimateSizeFactors(rat_deseq_dat_w_syn)
rld_w_syn <- rlog(rat_deseq_dat_w_syn, blind = FALSE)

rld_tib_w_syn <- as.data.frame(t(assay(rld_w_syn))) %>% 
  rownames_to_column(var = "samp_id")

gee_dat_w_syn <- rat_groups_w_syn %>% 
  inner_join(rld_tib_w_syn, by = "samp_id") %>% 
  arrange(animal) 

model_prep_w_syn <- gee_dat_w_syn %>%  
  pivot_longer(cols = starts_with("ENSRN"), 
               names_to = "gene_id",
               values_to = "expr_val") %>% 
  group_by(gene_id) %>%
  nest()

write_rds(model_prep_w_syn, here("data/expr_dat_w_syn.rds"))
```

## Control as baseline model
```{r}
# order by SRA run accession 
rat_groups_w_syn <- rat_groups %>% 
  arrange(samp_id) %>% 
  mutate(to_sep = samp_id) %>% 
  #filter(group != "syn_acth_els") %>% 
  separate(to_sep, into = c("region", "animal"), " ") %>%
  mutate(across(c(group, sex), as.factor),
         #region = ifelse(str_detect(samp_id, "Hip"), "Hip", "PFC"),
         region = as.factor(region),
         samp_id = str_replace_all(samp_id, fixed(" "), ""),
         animal = as.factor(animal)) %>% 
  mutate(treat_group = case_when(group == "acthar_els" | group == "syn_acth_els" ~ "ACTH",
                                 group == "dex_els" ~ "DEX",
                                 group == "ELS" ~ "ELS",
                                 group == "ctl" ~ "CTL"),
         treat_group = as.factor(treat_group)) %>% 
  arrange(animal) %>% 
  mutate(treat_group = fct_relevel(treat_group, c("CTL", "ACTH", "DEX", "ELS"))) # Everything is the same but switch CTL as first factor level


rat_deseq_dat_w_syn <- DESeqDataSetFromMatrix(countData = rat_dat,
                                              colData = rat_groups_w_syn,
                                              design = ~ group + sex)

keep_w_syn <- rowSums(counts(rat_deseq_dat_w_syn)) >= 10
rat_deseq_dat_w_syn <- rat_deseq_dat_w_syn[keep_w_syn,]

rat_deseq_dat_w_syn <- estimateSizeFactors(rat_deseq_dat_w_syn)
rld_w_syn <- rlog(rat_deseq_dat_w_syn, blind = FALSE)

rld_tib_w_syn <- as.data.frame(t(assay(rld_w_syn))) %>% 
  rownames_to_column(var = "samp_id")

gee_dat_w_syn <- rat_groups_w_syn %>% 
  inner_join(rld_tib_w_syn, by = "samp_id") %>% 
  arrange(animal) 

model_prep_w_syn <- gee_dat_w_syn %>%  
  pivot_longer(cols = starts_with("ENSRN"), 
               names_to = "gene_id",
               values_to = "expr_val") %>% 
  group_by(gene_id) %>%
  nest()

write_rds(model_prep_w_syn, here("data/expr_dat_w_syn_ctl_base.rds"))
```

# III. Run GEEs

The code to run both the Control and vehicle ELS models was written in R, however due to the memory and time required to run roughly 20,0000 models we packaged the code into a script and ran it onto the Vermont Advanced Computing Cluster (VACC). That code is included in the following chunk.

## vehicle ELS model
```{r}
#gee running script for the models excluding synactin
#first model will not have an interaction term, while the second model will

library(tidyverse)
library(here)
library(gee)

model_expr_df <- read_rds(here("data/expr_dat_w_syn.rds"))

run_gees <- function(model_df) {

  gee_df <- model_df %>% mutate(model = map(data, ~ gee(expr_val ~ treat_group + sex + region + treat_group:region,
                                                        id = animal,
                                                        corstr = "exchangeable",
                                                        data = .)))
  return(gee_df)

}

syn_w_interaction <- run_gees(model_df = model_expr_df)
write_rds(syn_w_interaction, here("results/syn_w_interaction_gee_els_v_all.rds"))

```

## Control Model
```{r}
#gee running script for the models excluding synactin
#first model will not have an interaction term, while the second model will

library(tidyverse)
library(here)
library(gee)

model_expr_df <- read_rds(here("data/expr_dat_w_syn_ctl_base.rds"))

run_gees <- function(model_df) {

  gee_df <- model_df %>% mutate(model = map(data, ~ gee(expr_val ~ treat_group + sex + region + treat_group:region,
                                                        id = animal,
                                                        corstr = "exchangeable",
                                                        data = .)))

}

syn_w_interaction <- run_gees(model_df = model_expr_df)
write_rds(syn_w_interaction, here("results/syn_w_interaction_gee.rds"))
```

# IV. Post-Process GEEs

## GEE Model with ELS as Baseline
```{r}
# Commented out as post-processed data is available in results directory.
# 
# els_gee <- read_rds(here("results/syn_w_interaction_gee_els_v_all.rds"))
# 
# els_gee_pvals <- get_gee_p(mod_obj = els_gee)
# els_gee_coefs <- add_coefs(els_gee_pvals, els_gee)
# 
# els_tibble <- els_gee_coefs %>%
#   map(as_tibble, rownames = "term") %>%
#   bind_rows(., .id = "gene_id") %>%
#   mutate(term = case_when(term == "(Intercept)" ~ "intercept",
#                           term == "treat_groupACTH" ~ "treat_group_acth",
#                           term == "treat_groupDEX" ~ "treat_group_dex",
#                           term == "treat_groupCTL" ~ "treat_group_ctl",
#                           term == "sexM" ~ "sex_m",
#                           term == "regionPFC" ~ "region_pfc",
#                           term == "treat_groupACTH:regionPFC" ~ "treat_group_acth_by_region_pfc",
#                           term == "treat_groupDEX:regionPFC" ~ "treat_group_dex_by_region_pfc",
#                           term == "treat_groupCTL:regionPFC" ~ "treat_group_ctl_by_region_pfc"))
# 
# 
# 
# els_anno <- get_gene_names(els_tibble, anno_tib = anno_genes)
# write_csv(els_anno, here("results/gee_degs/els_model_res.csv"))
els_anno <- read_csv(here("results/gee_degs/els_model_res.csv"))
```

## GEE Model with Control as Baseline
```{r}

# Commented out as post-processed data is available in results directory.
# ctl_gee <- read_rds(here("results/syn_w_interaction_gee.rds"))
# ctl_gee_pvals <- get_gee_p(mod_obj = ctl_gee)
# ctl_gee_coefs <- add_coefs(ctl_gee_pvals, ctl_gee)
# 
#  
# ctl_tibble <- ctl_gee_coefs %>% 
#   map(as_tibble, rownames = "term") %>% 
#   bind_rows(., .id = "gene_id") %>% 
#   mutate(term = case_when(term == "(Intercept)" ~ "intercept",
#                           term == "treat_groupACTH" ~ "treat_group_acth",
#                           term == "treat_groupDEX" ~ "treat_group_dex",
#                           term == "treat_groupELS" ~ "treat_group_els",
#                           term == "sexM" ~ "sex_m",
#                           term == "regionPFC" ~ "region_pfc",
#                           term == "treat_groupACTH:regionPFC" ~ "treat_group_acth_by_region_pfc",
#                           term == "treat_groupDEX:regionPFC" ~ "treat_group_dex_by_region_pfc",
#                           term == "treat_groupELS:regionPFC" ~ "treat_group_els_by_region_pfc"))
# 
# 
# ctl_anno <- get_gene_names(ctl_tibble, anno_tib = anno_genes)
# write_csv(ctl_anno, here("results/gee_degs/ctl_model_res.csv"))
ctl_anno <- read_csv(here("results/gee_degs/ctl_model_res.csv"))
```

# V. Make Figures

## Figure One
```{r prep-acth-data-for-venns, eval=TRUE, include=FALSE}
base_els_v_ctl_all <- get_model_values(els_anno, 
                                       treat_group_ctl, 
                                       direction = "all", 
                                       p_cutoff = TRUE)
base_ctl_v_acth_all <- get_model_values(ctl_anno, 
                                        treat_group_acth, 
                                        direction = "all", 
                                        p_cutoff = TRUE)
base_els_v_acth_all <- get_model_values(els_anno, 
                                        treat_group_acth, 
                                        direction = "all", 
                                        p_cutoff = TRUE) 
```

```{r ontology-acth, eval=TRUE, include=FALSE}
base_els_v_ctl_ont <- gost(query = base_els_v_ctl_all$gene_name,
                           organism = "rnorvegicus", 
                           correction_method = "fdr",
                           sources = "GO:BP")
base_ctl_v_acth_ont <- gost(query = base_ctl_v_acth_all$gene_name,
                            organism = "rnorvegicus", 
                            correction_method = "fdr",
                            sources = "GO:BP")
base_els_v_acth_ont <- gost(query = base_els_v_acth_all$gene_name,
                            organism = "rnorvegicus", 
                            correction_method = "fdr",
                            sources = "GO:BP")

base_els_v_ctl_ont_res <- base_els_v_ctl_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_name, evc_p_value = p_value)

base_els_v_acth_ont_res <- base_els_v_acth_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_name, eva_p_value = p_value)

base_ctl_v_acth_ont_res <- base_ctl_v_acth_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_name, cva_p_value = p_value)

```

```{r acth_venn, eval=TRUE, include=FALSE}
acth_base_ctl_all <- list(`CTL v. ELS` = base_els_v_ctl_all$gene_name,
                          `ACTH v. CTL` = base_ctl_v_acth_all$gene_name,
                          `ACTH v. ELS` = base_els_v_acth_all$gene_name)

acth_base_ctl_venn_all <- ggvenn(acth_base_ctl_all, 
                                 text_size = 7,
                                 show_percentage = FALSE)

ggsave(here("results/figures/acth_base_ctl_venn_all.png"),
       acth_base_ctl_venn_all,
       height = 10,
       width = 10,
       units = "in",
       dpi = 600)
```

```{r prep-dex-data-for-venns, eval=TRUE, include=FALSE}
base_els_v_ctl_all <- get_model_values(els_anno, 
                                       treat_group_ctl, 
                                       direction = "all", 
                                       p_cutoff = TRUE)
base_ctl_v_dex_all <- get_model_values(ctl_anno, 
                                       treat_group_dex, 
                                       direction = "all", 
                                       p_cutoff = TRUE)
base_els_v_dex_all <- get_model_values(els_anno, 
                                       treat_group_dex, 
                                       direction = "all",
                                       p_cutoff = TRUE) 
```

```{r ontology-dex, eval=TRUE, include=FALSE}

base_els_v_ctl_ont <- gost(query = base_els_v_ctl_all$gene_name,
                           organism = "rnorvegicus", 
                           correction_method = "fdr",
                           sources = "GO:BP")
base_ctl_v_dex_ont <- gost(query = base_ctl_v_dex_all$gene_name,
                           organism = "rnorvegicus", 
                           correction_method = "fdr",
                           sources = "GO:BP")
base_els_v_dex_ont <- gost(query = base_els_v_dex_all$gene_name,
                           organism = "rnorvegicus", 
                           correction_method = "fdr",
                           sources = "GO:BP")
base_els_v_ctl_ont_res <- base_els_v_ctl_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_name, evc_p_value = p_value)

base_els_v_dex_ont_res <- base_els_v_dex_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_name, evd_p_value = p_value)

base_ctl_v_dex_ont_res <- base_ctl_v_dex_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_name, cvd_p_value = p_value)


```

```{r dex-venn, eval=TRUE, include=FALSE}
dex_base_ctl_all <- list(`CTL v. ELS` = base_els_v_ctl_all$gene_name,
                         `DEX v. CTL` = base_ctl_v_dex_all$gene_name,
                         `DEX v. ELS` = base_els_v_dex_all$gene_name)

dex_base_ctl_venn_all <- ggvenn(dex_base_ctl_all, 
                                text_size = 7,
                                show_percentage = FALSE)

ggsave(here("results/figures/dex_base_ctl_venn_all.png"),
       dex_base_ctl_venn_all,
       height = 10,
       width = 10,
       units = "in",
       dpi = 600)
```

```{r combined-venn}

combined_venns <- acth_base_ctl_venn_all + dex_base_ctl_venn_all

ggsave(here("results/figures/figure_one.tiff"), 
       combined_venns,
       height = 8,
       width = 16,
       units = "in",
       dpi = 600)
```


## Figure Two

The data for these plots was retrieved from REVIGO

```{r prerevigo}
ctl_acth_shared_all <- base_els_v_acth_all %>% 
  filter(gene_name %in% base_els_v_ctl_all$gene_name)

ctl_acth_shared_all_ont <- gprofiler2::gost(query = ctl_acth_shared_all$gene_name,
                                            organism = "rnorvegicus",
                                            correction_method = "fdr",
                                            sources = c("GO:BP"))

ctl_acth_shared_all_ont$result %>%
  dplyr::select(term_id, p_value) %>% 
  write_csv(here("results/ontology/ctl_acth_shared_all_ont.csv"))

ctl_dex_shared_all <- base_els_v_dex_all %>% 
  filter(gene_name %in% base_els_v_ctl_all$gene_name)

ctl_dex_shared_all_ont <- gprofiler2::gost(query = ctl_dex_shared_all$gene_name,
                                           organism = "rnorvegicus",
                                           correction_method = "fdr",
                                           sources = "GO:BP")

ctl_dex_shared_all_ont$result %>% 
  select(term_id, p_value) %>% 
  write_csv(here("results/ontology/ctl_dex_shared_all_ont.csv"))
```

```{r revigo}

ctl_acth_shared_all_ont_plot <- semantic_plot(here("results/revigo_ontology/ctl_acth_shared_all_revigo.csv"), 
                                              title = "Shared CTL and ACTH DEG signal",
                                              subtitle = "All DEGs") +
  theme(plot.subtitle = element_blank(),
        plot.title = element_blank(),
        axis.title = element_blank(),
        axis.text = element_text(size = 15),
        legend.position = "bottom")


ctl_dex_shared_all_ont_plot <- semantic_plot(here("results/revigo_ontology/ctl_dex_shared_all_revigo.csv"), 
                                             title = "Shared CTL and DEX DEG signal",
                                             subtitle = "All DEGs",
                                             disp = 0.6) +
  theme(plot.subtitle = element_blank(),
        plot.title = element_blank(),
        axis.title = element_blank(),
        axis.text = element_text(size = 15),
        legend.position = "bottom")
```

```{r}
fig_two <- ctl_acth_shared_all_ont_plot + ctl_dex_shared_all_ont_plot

ggsave(here("results/figures/fig_two.png"),
       fig_two,
       height = 10,
       width = 20,
       units = "in",
       dpi = 600)
```

## Figure Three
```{r}
v_colors <- viridis(n = 5)

evc_eva_comb_ont <- full_join(base_els_v_ctl_ont_res, base_els_v_acth_ont_res, by = "term_name") %>% 
  mutate(evc_p_value = -log10(replace_na(evc_p_value, 0)),
         eva_p_value = -log10(replace_na(eva_p_value, 0))) %>% 
  mutate(across(contains("p_value"), ~ replace(., is.infinite(.), 0)))

evc_v_eva_comp_plot <- evc_eva_comb_ont %>% 
  ggplot(aes(x = evc_p_value, y = eva_p_value)) +
  geom_point() + 
  geom_abline(linetype = "dashed") +
  geom_point(data = evc_eva_comb_ont %>% filter(evc_p_value == 0),
             aes(x = evc_p_value, y = eva_p_value), color = v_colors[1], size = 5) +
  geom_point(data = evc_eva_comb_ont %>% filter(eva_p_value == 0),
             aes(x = evc_p_value, y = eva_p_value), color = v_colors[2], size = 5) +
  geom_point(data = evc_eva_comb_ont %>% filter(evc_p_value != 0 & eva_p_value != 0),
             aes(x = evc_p_value, y = eva_p_value), color = v_colors[5], size = 5) +
  geom_text_repel(data = evc_eva_comb_ont %>% filter(evc_p_value != 0 & eva_p_value != 0), 
                   aes(x = evc_p_value, y = eva_p_value, label = term_name),
                   force = 8,
                   size = 6) +
  labs(x = "Control v. ELS P-value (-log10)",
       y = "ACTH v. ELS P-value (-log10)") +
  theme_light() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 20),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 25))

evc_evd_comb_ont <- full_join(base_els_v_ctl_ont_res, base_els_v_dex_ont_res, by = "term_name") %>% 
  mutate(evc_p_value = -log10(replace_na(evc_p_value, 0)),
         evd_p_value = -log10(replace_na(evd_p_value, 0))) %>% 
  mutate(across(contains("p_value"), ~ replace(., is.infinite(.), 0)))

evc_v_evd_comp_plot <- evc_evd_comb_ont %>% 
  ggplot(aes(x = evc_p_value, y = evd_p_value)) +
  geom_point() + 
  geom_abline(linetype = "dashed") +
  geom_point(data = evc_evd_comb_ont %>% filter(evc_p_value == 0),
             aes(x = evc_p_value, y = evd_p_value), color = v_colors[3], size = 5) +
  geom_point(data = evc_evd_comb_ont %>% filter(evd_p_value == 0),
             aes(x = evc_p_value, y = evd_p_value), color = v_colors[2], size = 5) +
  geom_point(data = evc_evd_comb_ont %>% filter(evc_p_value != 0 & evd_p_value != 0),
             aes(x = evc_p_value, y = evd_p_value), color = v_colors[5], size = 5) +
  geom_text_repel(data = evc_evd_comb_ont %>% filter(evc_p_value != 0 & evd_p_value != 0), 
                   aes(x = evc_p_value, y = evd_p_value, label = term_name),
                   force = 8,
                   size = 6) +
  labs(x = "Control v. ELS P-value (-log10)",
       y = "Dex v. ELS P-value (-log10)") +
  theme_light() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 20),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 25))

fig_three <- evc_v_eva_comp_plot + evc_v_evd_comp_plot

ggsave(here("results/figures/figure_three.png"),
       fig_three,
       height = 10,
       width = 20,
       units = "in",
       dpi = 600)
```

## Figure Four

```{r acth-v-dex-ont-comp, eval=TRUE, include=FALSE}

ont_comp_combined <- full_join(base_els_v_dex_ont_res, base_els_v_acth_ont_res, by = "term_name") %>% 
  mutate(evd_p_value = -log10(replace_na(evd_p_value, 0)),
         eva_p_value = -log10(replace_na(eva_p_value, 0))) %>% 
  mutate(across(contains("p_value"), ~ replace(., is.infinite(.), 0)))

ont_comp_plot <- ont_comp_combined %>% 
  ggplot(aes(x = evd_p_value, y = eva_p_value)) +
  geom_point() + 
  geom_point(data = ont_comp_combined %>% 
               mutate(which_unique = case_when(evd_p_value == 0 ~ "ACTH Unique",
                                               eva_p_value == 0 ~ "Dex Unique",
                                               evd_p_value != 0 &
                                                 eva_p_value != 0 ~ "Shared")),
             aes(x = evd_p_value, y = eva_p_value, color = which_unique), size = 5) +
  geom_text_repel(data = ont_comp_combined %>% filter(evd_p_value != 0 & eva_p_value != 0), 
                   aes(x = evd_p_value, y = eva_p_value, label = term_name),
                   force = 8,
                   size = 6) +
  geom_abline(linetype = "dashed") +
  scale_color_viridis_d() +
  labs(x = "Dex v. ELS P-value (-log10)",
       y = "ACTH v. ELS P-value (-log10)") +
  theme_light() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 20),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 25))

ggsave(filename = here("results/figures/dex_v_acth.png"), 
       ont_comp_plot, 
       width = 12, 
       height = 12, 
       units = "in", 
       dpi = 600)
```

```{r split-unique-ontologies, eval=TRUE, include=FALSE}

eva_ont_res <- base_els_v_acth_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_id, term_name, eva_p_value = p_value)

evd_ont_res <- base_els_v_dex_ont$result %>% 
  as_tibble() %>% 
  dplyr::select(term_id, term_name, evd_p_value = p_value)

joined_ont <- full_join(evd_ont_res, eva_ont_res, by = c("term_name", "term_id")) %>% 
  mutate(evd_p_value = replace_na(evd_p_value, 0),
         eva_p_value = replace_na(eva_p_value, 0))

joined_ont %>% 
  filter(evd_p_value == 0) %>% 
dplyr::select(term_id, eva_p_value) %>% 
  write_csv(here("results/ontology/acth_spec_ont.csv"))

joined_ont %>% 
  filter(eva_p_value == 0) %>%
dplyr::select(term_id, evd_p_value) %>% 
  write_csv(here("results/ontology/dex_spec_ont.csv"))

```

```{r unique-ont-semantic-plots, eval=TRUE, include=FALSE}

dex_spec_plot <- semantic_plot(here("results/revigo_ontology/dex_spec_revigo.csv"), 
                               title = "DEX Specific Pathways",
                               subtitle = "",
                               disp = .10) +
  theme(plot.subtitle = element_blank(),
        plot.title = element_blank(),
        axis.title = element_blank(),
        axis.text = element_text(size = 20),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

ggsave(here("results/figures/dex_spec_plot.png"),
       dex_spec_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

acth_spec_plot <- semantic_plot(here("results/revigo_ontology/acth_spec_revigo.csv"), 
                                title = "ACTH Specific Pathways",
                                subtitle = "",
                                disp = 0.10) +
  theme(plot.subtitle = element_blank(),
        plot.title = element_blank(),
        axis.title = element_blank(),
        axis.text = element_text(size = 20),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 10),
        legend.position = "bottom")

ggsave(here("results/figures/acth_spec_plot.png"),
       acth_spec_plot,
       height = 8,
       width = 8,
       units = "in",
       dpi = 600)

```

```{r together-plot, fig.width='70%'}
fig_four <- ont_comp_plot / (acth_spec_plot + dex_spec_plot)

ggsave(here("results/figures/figure_four.png"),
       fig_four,
       height = 15,
       width = 20,
       units = "in",
       dpi = 600)

ggsave(here("results/figures/figure_four.svg"),
       fig_four,
       height = 15,
       width = 20,
       units = "in",
       dpi = 600)


```